\documentclass[10pt]{article}
\usepackage[margin=0.62in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\pagenumbering{gobble}
\setlist[itemize]{leftmargin=*,nosep}
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\titlerule]
\begin{document}
\begin{center}
{\LARGE Srikrishnaa Vadivel}\\
Computational Physicist \textbar{} First Principles \textbar{} HPC \textbar{} Scientific Software\\
\href{mailto:srikrishnaacareers@gmail.com}{srikrishnaacareers@gmail.com} \textbar{} 516-853-5663\\
\href{https://github.com/krishnaa423}{github.com/krishnaa423} \textbar{}
\href{https://leetcode.com/u/krishnaa42342/}{leetcode.com/u/krishnaa42342} \textbar{}
\href{https://hub.docker.com/u/krishnaa42342}{hub.docker.com/u/krishnaa42342}
\end{center}
\section{Summary}
Computational physics PhD researcher focused on first-principles calculations
of self-trapped excitons, scientific software, and high-performance simulation.
Experience includes leadership-class HPC, PETSc/SLEPc, MPI/OpenMP, Python/C++,
and ML-assisted materials workflows.
\section{Research}
\textbf{Yale University, PhD Researcher} \hfill 2021--present
\begin{itemize}
\item Perform first-principles calculations of self-trapped excitons using HPC
resources at Oak Ridge, Aurora, LBNL, and LLNL.
\item Build reproducible Linux, Bash, Python, C/C++, CMake, PETSc/SLEPc,
MPI/OpenMP, Docker, and Kubernetes workflows for large simulations.
\item Explore machine-learning surrogates and equivariant molecular models for
materials and molecular systems.
\end{itemize}
\section{Selected Technical Projects}
\begin{itemize}
\item \textbf{DOLFINx PDE Gallery}: weak forms for Poisson, heat, and
elasticity, plus solver/visualization scaffold.
\item \textbf{First-Principles LiF}: plane-wave pseudopotential Hamiltonian and
band plotting.
\item \textbf{Physics Action Notes}: path integrals, imaginary time, EM, GR,
QED/QCD, Standard Model, and strings from action principles.
\item \textbf{Meep Ring Resonator}: photonics FDTD geometry and source setup.
\end{itemize}
\section{Industry}
\textbf{Probe Technologies / Weatherford} \hfill 2019--2021\\
Built CUDA/OpenGL waveform processing and visualization software for acoustic
logging tools; also delivered embedded sensor logging firmware and FPGA logic.
\section{Education}
Yale University, PhD Electrical Engineering, 2021--present\\
Yale University, MPhil Electrical Engineering, 2023\\
Yale University, MS Electrical Engineering, 2023\\
Cornell University, MEng ECE, 2017--2018\\
Cornell University, BA ECE, 2013--2017
\section{Skills}
DFT workflows, PDEs, numerical linear algebra, PETSc, SLEPc, MPI, OpenMP,
Python, C++, CMake, Linux, CUDA, PyTorch, DOLFINx concepts, Meep concepts.
\end{document}
