\documentclass[10pt,letterpaper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[scale=0.84]{geometry}
\nopagenumbers{}
\setlength{\hintscolumnwidth}{2.35cm}

\name{Krishnaa}{Vadivel}
\title{Electrical Engineer | Semiconductor Devices | Photonics | FPGA Systems}
\email{srikrishnaa.careers@gmail.com}
\phone[mobile]{516-853-5663}
\social[linkedin]{sri-krishnaa-ece-phd}
\extrainfo{\href{https://github.com/krishnaa423}{GitHub: krishnaa423} \textbar{} \href{https://leetcode.com/u/krishnaa42342}{LeetCode: krishnaa42342} \textbar{} \href{https://hub.docker.com/u/krishnaa42342}{Docker Hub: krishnaa42342}}

\begin{document}
\makecvtitle

\section{Profile}
\cvitem{}{Electrical engineering PhD researcher with broad preparation across semiconductor physics, devices, integrated photonics, embedded systems, digital design, and scientific software. Combines theory-level understanding with implementation experience in FPGA/MCU systems, numerical device modeling, accelerator-enabled computation, and engineering tooling.}

\section{Research Experience}
\cventry{2021--present}{Research Assistant / PhD Researcher}{Yale University, Electrical Engineering}{}{}{\begin{itemize}%
\item Conduct research connecting materials-scale and device-relevant modeling, including first-principles excited-state methods, semiconductor physics, many-body theory, and scalable computational workflows.
\item Develop numerical and software infrastructure in Python and C++ for simulation and analysis on accelerator-enabled HPC systems, using MPI, OpenMP, CUDA, ROCm, PETSc, and SLEPc.
\item Serve as an embedded systems teaching assistant, supporting laboratory instruction and student work involving firmware, hardware interfaces, debugging, and instrumentation.
\item Maintain strong continuity between theory and engineering practice through coursework and self-developed notes in electromagnetism, signals/systems, semiconductor transport, optics, and device equations.
\item Co-authored a 2025 \textit{Journal of the American Chemical Society} paper and presented related APS work in 2024, 2025, and 2026 on self-trapped excitons and excited-state materials phenomena.
\end{itemize}}

\section{Professional Experience}
\cventry{2019--2021}{Software and Embedded Systems Engineer}{Probe Technologies Inc. / Weatherford Wireline Services}{}{}{\begin{itemize}%
\item Developed firmware and digital logic for sensor-logging and control functions in geological well tools using Lattice FPGA, PIC32, dsPIC, STM32, and C8051-class hardware.
\item Built CUDA-based processing and custom OpenGL visualization tools for large acoustic waveform datasets used in engineering analysis and field diagnostics.
\item Contributed host-side software and infrastructure using C\#, ASP-based services, and Microsoft SQL-backed data workflows.
\item Participated in board- and system-level engineering tasks including selective Altium PCB updates, oscilloscope-based verification, integration testing, and field deployment support.
\end{itemize}}
\cventry{2018--2019}{Photonics Technical Writer}{FindLight}{}{}{\begin{itemize}%
\item Produced technical articles on lasers, photonics components, optical systems, and engineering applications for a specialized industrial audience.
\end{itemize}}

\section{Selected Projects}
\cventry{}{FPGA AI Accelerator for ML Datapaths}{}{}{}{\begin{itemize}%
\item Implemented a compact Verilog matrix-multiply accelerator and verification flow to demonstrate datapath tradeoffs relevant to AI hardware acceleration.
\end{itemize}}
\cventry{}{Single-Cycle MIPS Processor}{}{}{}{\begin{itemize}%
\item Built a small Verilog CPU and self-checking Icarus Verilog test bench to demonstrate ISA-level control, datapath design, and reproducible digital verification.
\end{itemize}}
\cventry{}{Semiconductor Device Simulation}{}{}{}{\begin{itemize}%
\item Developed numerical treatments of Poisson, drift-diffusion, and pn-junction-style device equations to connect semiconductor theory with engineering-oriented simulation.
\end{itemize}}
\cventry{}{Integrated Photonics and FDTD Modeling}{}{}{}{\begin{itemize}%
\item Modeled resonator and band-pass style photonic structures with Meep-based FDTD workflows for integrated-optics exploration.
\end{itemize}}
\cventry{}{Robotic Hand and Embedded Robotics Work}{}{}{}{\begin{itemize}%
\item Built an EEG-driven robotic hand project in undergraduate embedded systems work; related work was published in Circuit Cellar.
\end{itemize}}
\cventry{}{Maze Mapping Robot}{}{}{}{\begin{itemize}%
\item Worked on FPGA- and algorithm-driven robotic navigation with wireless control and remote-station coordination in course-based robotics work.
\end{itemize}}

\section{Education}
\cventry{2021--present}{PhD, Electrical Engineering}{Yale University}{}{}{Ongoing research spanning computational materials, semiconductor-relevant modeling, and scientific software.}
\cventry{2023}{MPhil, Electrical Engineering}{Yale University}{}{}{}
\cventry{2023}{MS, Electrical Engineering}{Yale University}{}{}{}
\cventry{2017--2018}{MEng, Electrical and Computer Engineering}{Cornell University}{}{}{Included work in stochastic computing, semiconductor/device topics, and advanced EE design.}
\cventry{2013--2017}{BS, Electrical and Computer Engineering}{Cornell University}{}{}{Included strong preparation in embedded systems, robotics, controls, and hardware-software integration.}

\section{Selected Coursework}
\cvitem{Semiconductors}{Semiconductor Physics; Thin Film Science; drift-diffusion and device modeling foundations}
\cvitem{Photonics}{Lasers and Optoelectronics; Integrated Photonics}
\cvitem{Circuits and VLSI}{VLSI Design; Analog VLSI Design; stochastic-computing-related design work}
\cvitem{Systems}{Mathematics of Signals and Systems; Advanced Embedded Systems}
\cvitem{Foundations}{Graduate Quantum Mechanics; Solid State Physics; Many-Body Quantum Physics}

\section{Technical Skills}
\cvitem{Languages}{Python, C, C++, CUDA, JavaScript, Bash, PowerShell}
\cvitem{Hardware}{Verilog, FPGA, PIC32, dsPIC, STM32, C8051, sensor interfaces, PCB bring-up, oscilloscope debugging}
\cvitem{Simulation}{Semiconductor device modeling, FDTD photonics simulation, numerical PDE workflows}
\cvitem{Software}{OpenGL, C\#, ASP-style services, Microsoft SQL, Linux command line}
\cvitem{Scientific Computing}{MPI, OpenMP, PETSc, SLEPc, NumPy, pandas, SciPy, SymPy, matplotlib}
\cvitem{Platforms}{Docker, Docker Compose, Kubernetes, gcloud, Frontier, Frontera, Perlmutter}

\end{document}
