\documentclass[10pt]{article}
\usepackage[margin=0.62in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\pagenumbering{gobble}
\setlist[itemize]{leftmargin=*,nosep}
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\titlerule]
\begin{document}
\begin{center}
{\LARGE Srikrishnaa Vadivel}\\
Embedded Systems Engineer \textbar{} FPGA \textbar{} Robotics \textbar{} Sensor Logging
\end{center}
\section{Summary}
Embedded systems engineer with field-tested sensor logging, MCU firmware, FPGA
logic, robotics, and scientific instrumentation experience. Comfortable from
oscilloscope validation and low-level C through host-side visualization and data
systems.
\section{Experience}
\textbf{Probe Technologies / Weatherford, Software and Embedded Engineer} \hfill 2019--2021
\begin{itemize}
\item Programmed C8051-class microcontrollers and Lattice FPGA logic for
sensor logging in geological well tools.
\item Validated embedded systems with oscilloscopes, bench instrumentation, and
field deployments.
\item Built host-side CUDA/OpenGL software for large acoustic waveform
processing and visualization.
\end{itemize}
\textbf{Yale University, Embedded Systems Teaching Assistant / PhD Researcher} \hfill 2021--present
\begin{itemize}
\item Served as embedded systems TA while pursuing PhD research in
computational materials and scientific computing.
\item Used Linux, C/C++, Python, MPI/OpenMP, PETSc/SLEPc, and HPC systems for
simulation workflows.
\end{itemize}
\textbf{Cornell ECE Robotics Hand Project} \hfill 2017
\begin{itemize}
\item Built an embedded robotic hand project later published in Circuit Cellar.
\end{itemize}
\section{Portfolio Projects}
\begin{itemize}
\item \textbf{MIPS Processor}: Verilog single-cycle CPU and self-checking
Icarus Verilog test bench.
\item \textbf{Matrix-Multiply Accelerator}: small AI accelerator block with
start/done handshake and test bench.
\item \textbf{ROS 2 TurtleBot Simulation}: robotics simulation plan with
trajectory analysis artifacts.
\end{itemize}
\section{Education}
Yale University, PhD Electrical Engineering, 2021--present\\
Cornell University, MEng ECE, 2017--2018\\
Cornell University, BA ECE, 2013--2017
\section{Skills}
C, C++, Verilog/SystemVerilog, FPGA, MCU firmware, FreeRTOS concepts, SPI,
I2C, UART, ADC logging, oscilloscopes, Linux, Python, CUDA, OpenGL, Git.
\end{document}
