\documentclass[10pt,letterpaper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[scale=0.81]{geometry}
\nopagenumbers{}
\setlength{\hintscolumnwidth}{2.25cm}

\name{Krishnaa}{Vadivel}
\title{Software Engineer | Machine Learning | Distributed Computing}
\email{srikrishnaa.careers@gmail.com}
\phone[mobile]{516-853-5663}
\social[linkedin]{sri-krishnaa-ece-phd}
\extrainfo{\href{https://krishnaa423.github.io/industry-personal-website/}{Website} \textbar{} \href{https://github.com/krishnaa423}{GitHub: krishnaa423} \textbar{} \href{https://leetcode.com/u/krishnaa42342}{LeetCode: krishnaa42342} \textbar{} \href{https://hub.docker.com/u/krishnaa42342}{Docker Hub: krishnaa42342}}

\begin{document}
\makecvtitle

\section{Summary}
\cvitem{}{Software engineer and Yale PhD researcher building machine-learning, distributed-computing, and automation workflows in Python and C++. Experience spans CUDA/ROCm acceleration, national-lab HPC systems, numerical software, Linux-based tooling, and agentic development workflows using modern LLM APIs and local models.}

\section{Experience}
\cventry{2021--present}{PhD Research Assistant}{Yale University, Electrical Engineering}{}{}{\begin{itemize}%
\item Develop Python/C++ workflows for first-principles and many-body simulation, using MPI, OpenMP, PETSc, SLEPc, CUDA, ROCm, CMake, and Linux shell tooling across leadership-class HPC environments.
\item Build reusable distributed-computing and machine-learning workflows for materials and molecular problems on national-lab GPU clusters including Frontier, Frontera, and Perlmutter.
\item Work across research code, debugging, compiler-aware build workflows, documentation, and theory-to-implementation translation for scalable computational software.
\item Co-authored a 2025 \textit{Journal of the American Chemical Society} paper and presented APS talks in 2024, 2025, and 2026, demonstrating research output alongside production-style software work.
\end{itemize}}
\cventry{2019--2021}{Software and Embedded Systems Engineer}{Probe Technologies Inc. / Weatherford Wireline Services}{}{}{\begin{itemize}%
\item Built CUDA-accelerated software for sensor-data and waveform processing, diagnostic analytics, and engineering tooling for large field datasets.
\item Developed ASP.NET and Microsoft SQL Server workflows for internal software, full-stack web server management, and remote tool-calibration support.
\item Developed C\# GUI applications for preparing customer inputs and interacting with engineering workflows tied to deployed hardware systems.
\end{itemize}}
\cventry{2018--2019}{Photonics Technical Writer}{FindLight}{}{}{\begin{itemize}%
\item Wrote technical content translating specialized optics and photonics topics into clear engineering-facing explanations.
\end{itemize}}

\section{Selected Projects}
\cvitem{Equivariant Graph Neural Networks}{Built PyTorch Geometric workflows for molecular-property prediction with equivariant graph neural networks and graph-transformer-style modeling ideas.}
\cvitem{Agentic Coding and Scientific Automation}{Built LangChain-based workflows using OpenAI API models and local Ollama models to read documentation, generate structured inputs, and accelerate coding and research workflows.}
\cvitem{Distributed Scientific Tooling}{Reusable software workflows for simulation setup, engineering analysis, and container-oriented research infrastructure.}
\cvitem{GPU Data Systems}{CUDA-accelerated Python and C++ utilities for high-throughput data processing, diagnostics, and numerical inspection.}

\section{Education}
\cventry{2021--present}{PhD, Electrical Engineering}{Yale University}{}{}{}
\cventry{2023}{MPhil, Electrical Engineering}{Yale University}{}{}{}
\cventry{2023}{MS, Electrical Engineering}{Yale University}{}{}{}
\cventry{2017--2018}{MEng, Electrical and Computer Engineering}{Cornell University}{}{}{}
\cventry{2013--2017}{BS, Electrical and Computer Engineering}{Cornell University}{}{}{}

\section{Technical Skills}
\cvitem{Languages}{Python, C, C++, JavaScript, Bash, SQL}
\cvitem{Scientific Computing}{MPI, OpenMP, PETSc, SLEPc, NumPy, pandas, SciPy, SymPy, matplotlib}
\cvitem{Systems}{Linux, CMake, Docker, Docker Compose, Kubernetes, gcloud}
\cvitem{Platforms}{CUDA, ROCm, Frontier, Frontera, Perlmutter}
\cvitem{ML / Automation}{PyTorch, PyTorch Geometric, scikit-learn, LangChain, OpenAI API, Ollama, graph neural networks, graph transformers, agentic workflows}

\end{document}
