\documentclass[10pt,letterpaper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[scale=0.84]{geometry}
\nopagenumbers{}
\setlength{\hintscolumnwidth}{2.35cm}

\name{Krishnaa}{Vadivel}
\title{Embedded Systems Engineer | Firmware | FPGA | Robotics}
\email{srikrishnaa.careers@gmail.com}
\phone[mobile]{516-853-5663}
\social[linkedin]{sri-krishnaa-ece-phd}
\extrainfo{\href{https://github.com/krishnaa423}{GitHub: krishnaa423} \textbar{} \href{https://leetcode.com/u/krishnaa42342}{LeetCode: krishnaa42342} \textbar{} \href{https://hub.docker.com/u/krishnaa42342}{Docker Hub: krishnaa42342}}

\begin{document}
\makecvtitle

\section{Profile}
\cvitem{}{Embedded systems engineer with experience spanning firmware development, FPGA logic, robotics, instrumentation, and field validation. Background includes low-level development for sensing and logging platforms, board bring-up and debugging, and companion software for analysis and visualization around embedded hardware.}

\section{Professional Experience}
\cventry{2019--2021}{Software and Embedded Systems Engineer}{Probe Technologies Inc. / Weatherford Wireline Services}{}{}{\begin{itemize}%
\item Developed embedded functionality for geological well tools using Lattice FPGA, PIC32, dsPIC, STM32, and C8051-class hardware platforms.
\item Implemented sensor-logging and control-side logic and firmware for field-deployed systems operating in instrumentation-heavy environments.
\item Performed oscilloscope-based debugging, bench validation, and field testing to verify hardware-software integration and system behavior.
\item Supported selective PCB updates in Altium and related board-level engineering tasks as system requirements evolved.
\item Built companion host-side engineering tools using CUDA and OpenGL for waveform processing, visualization, and diagnostic workflows around the embedded stack.
\item Contributed additional internal software using C\#, ASP-style services, and Microsoft SQL-backed data workflows.
\end{itemize}}
\cventry{2021--present}{Embedded Systems Teaching Assistant / PhD Researcher}{Yale University}{}{}{\begin{itemize}%
\item Supported embedded systems laboratories and student projects involving firmware, hardware interfaces, debugging practices, and instrumentation workflows.
\item Continued broader engineering work in scientific computing and simulation while maintaining strong embedded-systems fluency.
\end{itemize}}

\section{Selected Projects}
\cventry{}{EEG-Driven Robotic Hand}{}{}{}{\begin{itemize}%
\item Built an embedded robotic-hand project in undergraduate ECE work, integrating sensing, actuation, and control; related work was published in Circuit Cellar.
\end{itemize}}
\cventry{}{Maze Mapping Robot with Wireless Control}{}{}{}{\begin{itemize}%
\item Worked on a robotics project combining navigation logic, remote-station control, and wireless coordination in a course setting.
\end{itemize}}
\cventry{}{Single-Cycle MIPS Processor}{}{}{}{\begin{itemize}%
\item Implemented a small Verilog CPU and self-checking test bench to demonstrate digital design, datapath organization, and reproducible verification.
\end{itemize}}
\cventry{}{Matrix-Multiply Accelerator}{}{}{}{\begin{itemize}%
\item Built a compact Verilog accelerator block with clear start/done control behavior and a simulation-backed test flow.
\end{itemize}}
\cventry{}{Host-Side Diagnostic and Visualization Tooling}{}{}{}{\begin{itemize}%
\item Developed CUDA/OpenGL-based utilities for analyzing and visualizing waveform data associated with embedded sensing and logging systems.
\end{itemize}}

\section{Education}
\cventry{2021--present}{PhD, Electrical Engineering}{Yale University}{}{}{Ongoing doctoral work; also served as an embedded systems teaching assistant.}
\cventry{2023}{MPhil, Electrical Engineering}{Yale University}{}{}{}
\cventry{2023}{MS, Electrical Engineering}{Yale University}{}{}{}
\cventry{2017--2018}{MEng, Electrical and Computer Engineering}{Cornell University}{}{}{Included advanced engineering coursework and embedded-adjacent systems work.}
\cventry{2013--2017}{BS, Electrical and Computer Engineering}{Cornell University}{}{}{Included embedded systems, robotics, and hardware-software integration foundations.}

\section{Selected Coursework}
\cvitem{Embedded}{Advanced Embedded Systems; laboratory-oriented firmware and systems work}
\cvitem{Signals and Systems}{Mathematics of Signals and Systems}
\cvitem{Hardware}{VLSI Design; Analog VLSI Design; digital and mixed engineering foundations}
\cvitem{Supporting Theory}{Semiconductor Physics; controls/robotics-adjacent systems exposure in ECE training}

\section{Technical Skills}
\cvitem{Languages}{C, C++, Python, Bash, JavaScript}
\cvitem{Hardware}{Verilog, FPGA, PIC32, dsPIC, STM32, C8051, sensor logging, embedded control}
\cvitem{Interfaces}{SPI, I2C, UART, hardware-software integration workflows}
\cvitem{Validation}{Oscilloscopes, bench instrumentation, field testing, board bring-up, Altium update support}
\cvitem{Software}{Linux, CUDA, OpenGL, C\#, ASP-style services, Microsoft SQL}

\end{document}
