\documentclass[10pt]{article}
\usepackage[margin=0.62in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\pagenumbering{gobble}
\setlist[itemize]{leftmargin=*,nosep}
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\titlerule]
\begin{document}
\begin{center}
{\LARGE Srikrishnaa Vadivel}\\
Software Engineer \textbar{} Scientific Computing \textbar{} Distributed Systems\\
\href{mailto:srikrishnaa@example.com}{srikrishnaa@example.com} \textbar{} GitHub: portfolio repos
\end{center}

\section{Summary}
Software engineer and Yale PhD researcher building scientific computing,
high-performance simulation, data visualization, and ML infrastructure. Strong
background in Python, C/C++, Linux, CUDA/OpenGL, MPI/OpenMP, Docker, Kubernetes,
and production engineering for embedded and server-side systems.

\section{Experience}
\textbf{Yale University, PhD Researcher} \hfill 2021--present\\
\begin{itemize}
\item Built first-principles workflows for self-trapped excitons using HPC
resources at Oak Ridge, Aurora, LBNL, and LLNL.
\item Developed Python/C++ automation around PETSc/SLEPc, MPI, OpenMP, CMake,
Linux shell tooling, containers, and parallel job execution.
\item Prototyped ML models for molecular and materials data, including EGNN
force models and diffusion-style generative workflows.
\end{itemize}
\textbf{Probe Technologies / Weatherford, Software and Embedded Engineer} \hfill 2019--2021\\
\begin{itemize}
\item Wrote ASP server and Microsoft database tooling for field data systems.
\item Built CUDA/OpenGL acoustic logging visualization software for processing
and displaying large waveform data sets.
\item Delivered embedded firmware for C8051-class MCUs and Lattice FPGA sensor
logging used in geological well tools; validated with oscilloscopes and field
tests.
\end{itemize}
\textbf{FindLight, Photonics Blogger} \hfill 2018--2019\\
\begin{itemize}
\item Wrote technical photonics articles translating optics products and
applications into clear engineering content.
\end{itemize}

\section{Projects}
\begin{itemize}
\item \textbf{DOLFINx PDE Gallery}: weak-form derivations, Poisson solver,
PyVista visualization, and docs in index notation.
\item \textbf{Meep Ring Resonator}: FDTD photonics simulation of a ring coupled
to a waveguide with field animation workflow.
\item \textbf{First-Principles LiF}: plane-wave Hamiltonian scaffold and band
plotting for DFT-style workflows.
\item \textbf{ROS 2 TurtleBot Simulation}: Docker-oriented Nav2/Gazebo plan
with trajectory analysis fallback.
\end{itemize}

\section{Education}
\textbf{Yale University}, PhD, Electrical Engineering \hfill 2021--present\\
\textbf{Cornell University}, MEng, Electrical and Computer Engineering \hfill 2017--2018\\
\textbf{Cornell University}, BA, Electrical and Computer Engineering \hfill 2013--2017

\section{Skills}
Python, C, C++, CUDA, OpenGL, Bash, Linux, CMake, PETSc, SLEPc, MPI, OpenMP,
Docker, Kubernetes, SQL Server, ASP, PyTorch, NumPy, SciPy, pandas, scikit-learn,
Hugging Face, Terraform, AWS, GCP.
\end{document}
