\documentclass[10pt]{article}
\usepackage[margin=0.62in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\pagenumbering{gobble}
\setlist[itemize]{leftmargin=*,nosep}
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\titlerule]
\begin{document}
\begin{center}
{\LARGE Srikrishnaa Vadivel}\\
Electrical Engineer \textbar{} Photonics \textbar{} Embedded Systems \textbar{} Scientific Computing\\
\href{mailto:srikrishnaacareers@gmail.com}{srikrishnaacareers@gmail.com} \textbar{} 516-853-5663\\
\href{https://github.com/krishnaa423}{github.com/krishnaa423} \textbar{}
\href{https://leetcode.com/u/krishnaa42342/}{leetcode.com/u/krishnaa42342} \textbar{}
\href{https://hub.docker.com/u/krishnaa42342}{hub.docker.com/u/krishnaa42342}
\end{center}
\section{Summary}
Electrical engineer with Cornell ECE training, photonics communication,
embedded systems delivery, FPGA/MCU experience, and current Yale PhD work in
computational materials and high-performance scientific software.
\section{Experience}
\textbf{Yale University, PhD Researcher / Embedded Systems TA} \hfill 2021--present
\begin{itemize}
\item Research first-principles self-trapped excitons using HPC systems and
scientific software stacks.
\item Teach and support embedded systems concepts spanning firmware,
instrumentation, and debugging.
\end{itemize}
\textbf{Probe Technologies / Weatherford, Software and Embedded Engineer} \hfill 2019--2021
\begin{itemize}
\item Developed embedded sensor logging firmware and Lattice FPGA logic for
geological well tools.
\item Built CUDA/OpenGL acoustic waveform processing and visualization tooling.
\item Contributed ASP and Microsoft database software for field data workflows.
\end{itemize}
\textbf{FindLight, Photonics Blogger} \hfill 2018--2019
\begin{itemize}
\item Wrote clear technical content on photonics products, optics, and
applications.
\end{itemize}
\section{Projects}
\begin{itemize}
\item Verilog MIPS CPU and matrix-multiply accelerator with Icarus test benches.
\item Meep ring resonator FDTD model for integrated photonics simulation.
\item DOLFINx PDE notes and solver scaffold for finite-element methods.
\item Robotic hand embedded project published in Circuit Cellar.
\end{itemize}
\section{Education}
Yale University, PhD Electrical Engineering, 2021--present\\
Yale University, MPhil Electrical Engineering, 2023\\
Yale University, MS Electrical Engineering, 2023\\
Cornell University, MEng Electrical and Computer Engineering, 2017--2018\\
Cornell University, BA Electrical and Computer Engineering, 2013--2017
\section{Skills}
Circuits, embedded C, Verilog, FPGA, MCUs, photonics, signal processing,
OpenGL, CUDA, Python, C++, Linux, HPC, numerical methods.
\end{document}
